\begin{thebibliography}{7} 

\bibitem{manifesto} Kent Beck, Alistair Cockburn, Martin Fowler, et al. \textit{Agile Manifesto}. http://www.agilemanifesto.org;
\bibitem{retrospectives} Esther Derby, Diana Larsen. \textit{Agile Retrospectives: Making Good Teams Great}. Dallas: The Pragmatic Bookshelf, 2006.
\bibitem{funRetrospectives} Paulo Caroli, Taina Caetano. \textit{Fun Retrospectives: Activities and ideas for making agile retrospectives more engaging}. Leanpub, 2014. https://leanpub.com/funretrospectives
\bibitem{handRetrospectives} Patrick Kua. \textit{The Retrospective Handbook: A guide for agile teams}. Leanpub, 2013. https://leanpub.com/the-retrospective-handbook
\bibitem{lean} Taiichi Ohno, Norman Bodek. \textit{Toyota Production System: Beyond Large-Scale Production}. Productivity Press, 1988. https://books.google.com.br/books?id=7\_-67SshOy8C
\bibitem{brainwriting} Greene, R. J. \textit{Brainwriting: An effective way to create more ideas}. The Quality Circles Journal 10 (1987): 33-36.
\bibitem{versionOne} Version One. \textit{8th Annual State of Agile Survey}. Alpharetta: Version One, 2013. http://www.versionone.com/pdf/2013-state-of-agile-survey.pdf
\bibitem{scrumAlliance} Scrum Alliance. \textit{The 2015 State of Scrum Report}. Westminster: Scrum Alliance, 2015. https://www.scrumalliance.org/why-scrum/state-of-scrum-report/2015-state-of-scrum
\bibitem{poussard} Pascal Poussaard. \textit{Classifying Retrospectives to get the best of it}. 2014. http://www.benlinders.com/2014/guest-blog-classifying-retrospectives-to-get-the-best-of-it

\end{thebibliography}
